Block Bootstrap for Time Series

### 2022-01-31 ARSimulation.Rmd
Removed Some Code from Beginning

Simulates, prints, and plots auto-regressive process of order 1 with ar = 0.5 and size = 100
```{r, echo = FALSE}
ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
ts.sim
plot(ts.sim)
```

Splits time series into ten blocks of size 10 and stores them in a list
```{r, echo = False}
ts.blocks <- list(ts.sim[c(1 : 10)], ts.sim[c(11 : 20)], ts.sim[c(21 : 30)], ts.sim[c(31 : 40)], ts.sim[c(41 : 50)], ts.sim[c(51 : 60)], ts.sim[c(61 : 70)], ts.sim[c(71 : 80)], ts.sim[c(81 : 90)], ts.sim[c(91 : 100)])
ts.blocks
```

Randomly samples 10 non-overlapping blocks (with replacement) from ts.blocks, creating a single bootstrapped time series
```{r, echo = False}
ts.boot1 <- sample(ts.blocks, 10, replace = T)
ts.boot1
class(ts.boot1)
```

ts.boot1 is a list of vectors and does not work with the plot() function, so we use a nested loop to store the values in ts.boot2, a simpler numeric vector
```{r, echo = False}
ts.boot2 <- c()
for(i in 1 : 10) {
  for(j in 1 : 10) {
    ts.boot2 <- c(ts.boot2, ts.boot1[[i]][[j]])
  }
}
ts.boot2
class(ts.boot2)
```

Ts.boot2 is plotted
```{r, echo = False}
plot(ts.boot2, type = "l")
```
We need to start with a sample of a certain size B of consecutive points from a time series ts.series. First we need to randomly select a single point in the time series, and we can do this by selecting a number between 1 and 100.

>>>>

We need to start with a sample of a certain size B of consecutive points from a time series ts.series. First we need to randomly select a single point in the time series, and we can do this by selecting a number between 1 and 100.
